---
title: "A/B Testing"
author: "Nazmul"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Bayesian A/B testing offers significant advantages over frequentist approaches. In frequentist tests, point estimates are used, leading to interpretation challenges. Statisticians must conduct power tests, communicate results to non-technical stakeholders, and often struggle with interpretability. In contrast, Bayesian A/B testing enhances interpretability by providing direct probabilities of one variant's superiority over another. It replaces p-values with these probabilities, making it easier to understand the results. Bayesian tests offer posterior distributions for parameters, allowing for various summarization methods. They are also robust against data "peeking" and maintain validity if a test is halted prematurely.  



# Case Study  
### Scenario  
A fast-food chain plans to add a new item to its menu. However, they are still undecided between three possible marketing campaigns for promoting the new product. In order to determine which promotion has the greatest effect on sales, the new item is introduced at locations in several randomly selected markets. A different promotion is used at each location, and the weekly sales of the new item are recorded for the first four weeks.  

## Goal
Evaluate A/B testing results and decide which marketing strategy works the best.

## Columns   
MarketID: unique identifier for market  
MarketSize: size of market area by sales  
LocationID: unique identifier for store location  
AgeOfStore: age of store in years  
Promotion: one of three promotions that were tested  
week: one of four weeks when the promotions were run  
SalesInThousands: sales amount for a specific LocationID, Promotion, and week  


### required libries 

```{r}
library(tidyverse)
library(bayesAB)
```


```{r}
dt <- read.csv("WA_Marketing-Campaign.csv")
```

### EDA  

```{r}
summary(dt)  

glimpse(dt)
```

```{r}
dt$Promotion <- as.character(dt$Promotion)
```


As we can see from this chart, the promotion group 3 has the largest aggregate sales amount (36%). However, each promotion group takes roughly one third of the total sales during the promotion weeks.  


```{r}
#grouping data by Promotion
png(filename="prom_vs_perct.png", res=500, width=3312, height=1600)
prom <- dt %>%
  group_by(Promotion) %>%
  summarize(Sales=sum(SalesInThousands))%>%
  mutate(Percentage=round(Sales/sum(Sales)*100)) 

prom %>% 
  ggplot(aes(x= Promotion, y = Percentage, fill= Promotion)) + 
  geom_bar(stat = "identity") +  scale_fill_hue(labels = c("Prom 1", "Prom 2", "Prom 3")) + geom_text(aes(label = Percentage)) +
theme_minimal() +
theme(axis.text.x = element_blank(),
axis.title.x = element_blank(),
panel.grid = element_blank())
```



```{r}
png(filename="marsize.png", res=500, width=3312, height=1600)

msize <- dt %>%
  group_by(Promotion, MarketSize) %>%
  summarize(count= n()) 

msize %>% ggplot(aes(x= Promotion, y = count, fill= MarketSize)) + 
  geom_bar(stat = "identity", position="dodge") +
  theme_minimal() +
theme(panel.grid = element_blank())
```


The graph reveals that the proportion of market size for each promotion is more or less same comparing to others.    

```{r}
#normality check
shapiro.test(dt$SalesInThousands[dt$Promotion=="1"])
shapiro.test(dt$SalesInThousands[dt$Promotion=="2"])
shapiro.test(dt$SalesInThousands[dt$Promotion=="3"])

# mean, standard deviation
mean(dt$SalesInThousands[dt$Promotion=="1"])  
mean(dt$SalesInThousands[dt$Promotion=="2"])  
mean(dt$SalesInThousands[dt$Promotion=="3"])  

sd(dt$SalesInThousands[dt$Promotion=="1"])  
sd(dt$SalesInThousands[dt$Promotion=="2"])  
sd(dt$SalesInThousands[dt$Promotion=="3"])  
```

Since the distribution of sales follow normality   

```{r}
prom_1 <- rnorm(172, 58.09901, 16.55378)
prom_2 <- rnorm(188, 47.32941, 15.10895)
prom_3 <- rnorm(188, 55.36447, 16.76623)
```

```{r}
pm12 <- bayesTest(prom_1, prom_2, 
          priors = c('mu' = 5, 'lambda' = 2, 'alpha' = 3, 'beta' = 1), distribution = 'normal')
pm12
```


```{r}
summary(pm12)
```


```{r}
plot(pm12)
```





```{r}
pm13 <- bayesTest(prom_1, prom_3, 
          priors = c('mu' = 5, 'lambda' = 1, 'alpha' = 3, 'beta' = 1),
                 distribution = 'normal')
pm13
```

```{r}
summary(pm13)
```


```{r}
plot(pm13)
```




Promotion 1 outperform promotion 2, and 3.  


